### 2014-07-23 MS.tex
italics for names in the ref list

51. Wahlberg N, Rubinoff D (2011) Vagility across Vanessa (Lepidoptera:
Nymphalidae): mobility in butterfly species does not inhibit the
formation and persistence of isolated sister taxa. Syst Entomol 36:
362--370.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2010.00566.x}{10.1111/j.1365-3113.2010.00566.x}.

52. M\"uller CJ, Wahlberg N, Beheregaray LB (2010) `After Africa': the
evolutionary history and systematics of the genus Charaxes Ochsenheimer
(Lepidoptera: Nymphalidae) in the Indo-Pacific region. Biol J Linn Soc
100: 457--481.
doi:\href{http://dx.doi.org/10.1111/j.1095-8312.2010.01426.x}{10.1111/j.1095-8312.2010.01426.x}.

53. Aduse-Poku K, Vingerhoedt E, Wahlberg N (2009) Out-of-Africa again:
a phylogenetic hypothesis of the genus Charaxes (Lepidoptera:
Nymphalidae) based on 5 gene regions. Mol Phylogenet Evol 53: 463--478.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.06.021}{10.1016/j.ympev.2009.06.021}.

>>>>

51. Wahlberg N, Rubinoff D (2011) Vagility across \textit{Vanessa} (Lepidoptera:
Nymphalidae): mobility in butterfly species does not inhibit the
formation and persistence of isolated sister taxa. Syst Entomol 36:
362--370.
doi:\href{http://dx.doi.org/10.1111/j.1365-3113.2010.00566.x}{10.1111/j.1365-3113.2010.00566.x}.

52. M\"uller CJ, Wahlberg N, Beheregaray LB (2010) `After Africa': the
evolutionary history and systematics of the genus \textit{Charaxes} Ochsenheimer
(Lepidoptera: Nymphalidae) in the Indo-Pacific region. Biol J Linn Soc
100: 457--481.
doi:\href{http://dx.doi.org/10.1111/j.1095-8312.2010.01426.x}{10.1111/j.1095-8312.2010.01426.x}.

53. Aduse-Poku K, Vingerhoedt E, Wahlberg N (2009) Out-of-Africa again:
a phylogenetic hypothesis of the genus \textit{Charaxes} (Lepidoptera:
Nymphalidae) based on 5 gene regions. Mol Phylogenet Evol 53: 463--478.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.06.021}{10.1016/j.ympev.2009.06.021}.
